Application of Network Flow and Linear Programming to Scheduling of Clinicians

### 2019-08-19 paper/paper.results.tex
Update division runtime table and rephrase

Lastly, we analyze the effect of increasing the number of divisions on the runtime of the program. Table \ref{tbl:runtime-divisions-comparison} presents the runtime for $D = \{1, 2, 3\}$ divisions and $C = \{10, 20, 30, 50\}$ clinicians in total across all divisions. For 2 divisions, a roster of more than 20 clinicians becomes impractical, if all constraints must be satisfied, but the runtime can be improved if we allow consecutive blocks to be assigned. For 3 divisions, the problem becomes impractical faster, with any more than 10 clinicians leading to unreasonable runtime for finding an optimal solution, and the problem cannot be improved by relaxing the consecutive blocks constraint.

>>>>

Lastly, we analyze the effect of increasing the number of divisions on the runtime of the program. Table \ref{tbl:runtime-divisions-comparison} presents the runtime for $D = \{1, 2, 3\}$ divisions and $C = \{10, 20, 30, 50\}$ clinicians in total across all divisions. For 2 divisions, a roster of more than 20 clinicians becomes impractical to solve, as searching requires more than 24 hours. For 3 divisions we can see issues with runtime occur earlier, where configurations of more than 10 clinicians are unable to be solved in 24 hours. When relaxing the consecutive blocks constraint, we see a great improvement in runtime for 2 and 3 divisions, and even a schedule for 50 clinicians or more can be generated.

### 2019-08-19 paper/tbl/runtime_divisions.tex
Update division runtime table and rephrase

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		&       \multicolumn{4}{c|}{Number of Divisions}        \\ \hline
		Number of Clinicians &  1   &   2    & 2 (Consecutive Blocks Allowed) &  3   \\ \hline
		10          & 0.22 &  0.51  &              0.26              & 1.49 \\ \hline
		20          & 0.42 & 139.42 &              0.50              &     \\ \hline
		30          & 0.63 &   -    &              0.90              &     \\ \hline
		50          & 1.06 &   -    &              1.30              &     \\ \hline
	\end{tabular}
	\caption{Comparison of program runtime (in seconds) for different number of divisions and total clinicians. ``-'' indicates that a solution was not found after 24 hours.}
	\label{tbl:runtime-divisions-comparison}%
\end{table}

>>>>

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		                                      & \multicolumn{5}{c|}{Number of Divisions} \\ \hline
		\makecell[l]{Number of \\ Clinicians} &  1   &   2   & 2 (CBA) &  3   & 3 (CBA)  \\ \hline
		                 10                   & 0.18 & 0.94  &  0.24   & 2.02 &   0.30   \\ \hline
		                 20                   & 0.33 & 13.84 &  0.42   &      &   1.17   \\ \hline
		                 30                   & 0.51 &   -   &  0.68   &      &   0.93   \\ \hline
		                 50                   & 0.83 &   -   &  1.12   &      &   1.55   \\ \hline
	\end{tabular}
	\caption{Comparison of program runtime (in seconds) for different number of divisions and total clinicians. ``-'' indicates that a solution was not found after 24 hours. ``CBA'' indicates that \underline{c}onsecutive \underline{b}locks were \underline{a}llowed for these schedules.}
	\label{tbl:runtime-divisions-comparison}%
\end{table}
